---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# chainr

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
<!-- badges: end -->

## `chain`

When working with relational data, it's easier to think of data frames being chained together. You can for example create a `chain` list as below.

```{r}
library(chainr)
usa <- chain(
      state_stats = as.data.frame(state.x77),
      state_info = data.frame(name = state.name,
                              abb = state.abb,
                              division = state.division,
                              region = state.region),
      arrests = USArrests
    )
str(usa)
```

Then you can apply some familiar `dplyr` verbs, however you have an additional argument to supply to reference which dataset(s). 

```{r, warning = FALSE, message = FALSE}
library(dplyr)
usa %>% 
  select_in(arrests, Murder) %>% 
  str()
```

```{r, warning = FALSE, message = FALSE}
usa %>% 
  select_links(starts_with("state")) %>% 
  str()
```

Technically chain can hold objects that are not data frames. 
A tiny difference to just using `list` is that it evaluates
sequentially so you can refer to an element in the list 
defined in previous lines. 


```{r, message = FALSE, warning = FALSE}
library(rsample)
library(tidytuesdayR)
set.seed(1)
coffee <- chain(
  data = tt_load(2020, week = 28)$coffee,
  split = initial_split(data, prop = 0.8),
  train = training(split),
  test = testing(split),
  folds = vfold_cv(train, v = 5)
)

```




## Other related works

The approach in `chainr` is a really simple way of dealing with in-memory relational database. Alternatively, you can create a mock SQL database and work with it using `dbplyr`. 

A chain is a simple list. A more general list manipulation can be found in `rlist`.
